---
title: "Data607-HW9"
author: "Santosh Manjrekar"
date: "October 27, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, eval=TRUE}
suppressMessages(suppressWarnings(library('tidyverse')))
suppressMessages(suppressWarnings(library('httr')))
suppressMessages(suppressWarnings(library('jsonlite')))
```

## Accessing NYT API

I put my key into a line of code that is not included on the printout.
```{r, key ,eval=TRUE, include=FALSE}
key <- "***************"
```


I selected the API for the most veiwed Science articles from the last day, you can see that reflected in the url: "/mostviewed/Science/1.json" as the '1' before the josn file extension denotes number of days. NYT gave the option of 1, 7, or 30. I chose 1 because the emphasis was extracting the data from the API and putting the data in the json into a dataframe, not neccessarily a large data frame.

```{r, get, eval=TRUE}
nyt_url <- 'https://api.nytimes.com/svc/mostpopular/v2/mostviewed/Science/1.json' # the url following the NYT's instructions.
nyt_mp <- nyt_url %>% GET(add_headers('api-key'=key)) %>% content(as='text') %>% fromJSON(simplifyDataFrame = TRUE) # The key is in a hidden line of code.
# reading as text here turned out to be the easiest route since
# fromJSON() will automatically put the json file into a dataframe when 'simplifyDataFrame = TRUE'.
nyt_mp_df <- nyt_mp$results
head(nyt_mp_df)
```

####Conclusion:
I was able to call NY times website using their web API. I searched for most viewed science articles in last one day  and I found 6 articles and information around those articles. Looks like ble to use web-api is a very helpful skill.