---
title: "Data607-Assignment3"
author: "Santosh Manjrekar"
date: "September 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("stringr")
```

### Load the raw data while we are at it.
```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
raw.data
```
###Copy the introductory example. The vector name stores the extracted names.
```{r}
names <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
names
```

###1. Use the tools of this chapter to rearrange the vector so that all the elements conform to the standard first_name last_name.

The first regex I use ",.+$" identifies a string of one or more characters between a comma and the end of the string. This is to pull Monte Burns and Homer Simpson. Next is to extract a string of one or more characters between a period and a space, "\..+", this is for Rev. Lovejoy and Dr. Hibbert. Finally for Moe and Ned, the regex extracts exactly 3 characters between the start of the string and a space with no period, "^.[^\\.]{2}".

For the last names there were two patterns, the last name ended in a comma in the case of Homer and Monte, ".+," or the last name was 7 or 8 characters between a space and the end of the string for everyone else, "[[:blank:]].{7,8}".

I used for loops to take out unwanted spaces and punctuation marks.
```{r}
first_name <- str_extract_all(names, ",.+$|\\..+ |^.[^\\.]{2} ")
# Clean up the data a little by getting rid of punctuation and leading spaces
for(i in 1:length(first_name)){
  first_name[i] = gsub(", ", "", first_name[i])
  first_name[i] = gsub("\\. ", "", first_name[i])
  first_name[i] = gsub(" ", "", first_name[i])
# Instead of dropping the C. from Monte's name. I opted to keep it in, as I have a friend that does this on his social media and uses it as his pen name.
  first_name[i] = gsub("CM", "C. M", first_name[i])
}

last_name <- str_extract_all(names, ".+,|[ [:blank:]].{7,8}$")
for(i in 1:length(last_name)){
  last_name[i] = gsub(",", "", last_name[i])
}

names_df <-data.frame(name = paste(first_name,last_name))
names_df
```

####2. Create a logical vector to indicate if the character has a title.

The titles are either 2 or 3 letters long and are listed first, so I used srt_detect to start at the start of the string and look for three or 2 characters between a period, "^.{3}\.".|^.{2}\.".

```{r}
title <- str_detect(names, "^.{3}\\.|^.{2}\\.")
names_df <- cbind(names_df, title = title)
names_df
```
####3.Create a logical vector indicacting whether a character has a second name.

What makes Monte Burns different is his name is the only one with a comma and a period, so I used str_detect to look for strings with at least one character between a comma and period ",.+\.".
```{r}
second <- str_detect(names, ",.+\\.")
names_df <- cbind(names_df, scnd_nm = second)
names_df
```

####Chapter 8 Problem 4
```{r}
test_list <- as.character(c("5$" , "$5", "five$", "7,134,689$","at", "dab", "dAb" , "DaB" ,"band", "banana", "homework", 'homework.doc', "homework.txt", "txt", ".txt" , "7/4/76", "07/04/76", "07/04/1776", "07-04-1776", "<link>rpubs.com</link>", "<bold>Got It!</link>"))
test_list
```

###Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

1.[0-9]+\$ one or more digits 0 to 9 followed by a dollar sign.

```{r}
dollar <- str_detect(test_list, "[0-9]+\\$")
dollar <- cbind(test_list,dollar)
dollar
```

2. \b[a-z]{1,4}\b detects if a string contains 1 to 4 lower case letters bordered by a non-word character.

```{r}
words <- str_detect(test_list, "\\b[a-z]{1,4}\\b")
words <- cbind(test_list,words)
words
```

3. .*?\.txt$ checks the end of a string for a .txt that may or may not have characters before the ".".

```{r}
txt <- str_detect(test_list, ".*?\\.txt?")
txt <- cbind(test_list,txt)
txt

```

4. \d{2}/\d{2}//d{4} detects exactly 2 digits then a  then exactly two digits then a  then exactly 4 digits. This checks for a formatted dd\mm\yyyy or mm\dd\yyyy date depending if you are in the US or not.

```{r}
dates <- str_detect(test_list, "\\d{2}/\\d{2}/\\d{4}")
dates <- cbind(test_list,dates)
dates
```

5. <(.+?)>.+?</\1> this checks for html tags by capturing a string between < > that may or may not have a string between and matching it to a </ > with the same captured string in the braket.
```{r}
html <- str_detect(test_list, "<(.+?)>.+?</\\1>")
html <- cbind(test_list,html)
html
```

###Extra Credit Problem

```{r}
regex_code <- c("clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr")
```

####I tried a bunch of stuff then I deciced to look at different letter cases and I noticed this:

```{r}
upper <- str_extract_all(regex_code ,"[[:upper:]]")
upper 
```


